Impact of switching bug trackers: a case study on a medium-sized open source project

### 2019-03-05 article/article.tex
Fix compilation.

The highest peak is in 2015, after the first beta release of version 8.5. This was the first release in more than two years and it contained five big new features (``the result of five specific long-term projects''\footnote{Quote from \url{https://coq.inria.fr/refman/credits.html##credits-version-8-5}. The next quotes are coming from the following sections of the same chapter of the Coq reference manual.}). Stabilizing these features and their (unplanned) interactions required more than a year of testing and three beta releases. The 8.5 release was both hard on developers, who found the release cycle too long, and on users, who were impacted by many compatibility issues. Consequently, a different approach was taken for the following releases: versions 8.6, 8.7 and 8.8 were ``developed on a time-based development cycle'' and contain ``the result of refinements, stabilization of features and cleanups of the internals of the system along with a few new features''. Attention was given to regression testing: changes were systematically tested by building a selection of the largest Coq projects. Therefore, it is not surprising that these frequent releases are correlated to smaller peaks of new bug reports.

@@

%\noindent\footnotesize{\textbf{Acknowledgements.}}
%We would like to thank Ambre Williams for valuable advice and help on the design and implementation of the data analyses and C\'ecile Rottner for general advice, support, and proof-reading.
%We would like to thank Andriy Berestovskyy for providing the Bugzilla import tool, and Martin Michlmayr for doing the first steps in porting our modifications upstream.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{bib}
%
\end{document}

>>>>

The highest peak is in 2015, after the first beta release of version
8.5. This was the first release in more than two years and it
contained five big new features (``the result of five specific
long-term projects''\footnote{Quote from
  \url{https://coq.inria.fr/distrib/V8.9.0/refman/credits.html\#credits-version-8-5}. The
  next quotes are coming from the following sections of the same
  chapter of the Coq reference manual.}). Stabilizing these features
and their (unplanned) interactions required more than a year of
testing and three beta releases. The 8.5 release was both hard on
developers, who found the release cycle too long, and on users, who
were impacted by many compatibility issues. Consequently, a different
approach was taken for the following releases: versions 8.6, 8.7 and
8.8 were ``developed on a time-based development cycle'' and contain
``the result of refinements, stabilization of features and cleanups of
the internals of the system along with a few new features''. Attention
was given to regression testing: changes were systematically tested by
building a selection of the largest Coq projects. Therefore, it is not
surprising that these frequent releases are correlated to smaller
peaks of new bug reports.

@@

\noindent\footnotesize{\textbf{Acknowledgements.}}
We would like to thank Ambre Williams for valuable advice and help on the design and implementation of the data analyses and C\'ecile Rottner for general advice, support, and proof-reading.
We would like to thank Andriy Berestovskyy for providing the Bugzilla import tool, and Martin Michlmayr for doing the first steps in porting our modifications upstream.

%
% ---- Bibliography ----
\bibliography{bib}
\bibliographystyle{IEEEtran}
%
\end{document}
